Item Construction Rules Revisited: Learnings from Measurement of Latent Variables with Gold Standard Items

### 2025-07-28 analysis/secondary_analyses.qmd
Built site for gh-pages

fit_df <- bind_rows(
  data.frame(as.list(fitMeasures(fit1A6))) |> mutate(measure = "age", categories = "6"),
  data.frame(as.list(fitMeasures(fit1A2))) |> mutate(measure = "age", categories = "2"),
  data.frame(as.list(fitMeasures(fit1G6))) |> mutate(measure = "height", categories = "6"),
  data.frame(as.list(fitMeasures(fit1G2))) |> mutate(measure = "height", categories = "2"),
  data.frame(as.list(fitMeasures(fit1Ge6))) |> mutate(measure = "weight", categories = "6"),
  data.frame(as.list(fitMeasures(fit1Ge2))) |> mutate(measure = "weight", categories = "2")
) |>
  pivot_longer(!c(measure, categories), names_to = "statistic", values_to = "est") |>
  filter(statistic %in% c("chisq.scaled", "pvalue.scaled", "df.scaled", "cfi.scaled", "rmsea.scaled", "srmr")) |>
  mutate(statistic = case_match(statistic, "chisq.scaled" ~ "$\\chi^2$", "pvalue.scaled" ~ "p", "df.scaled" ~ "df", "cfi.scaled" ~ "CFI", "rmsea.scaled" ~ "RMSEA", "srmr" ~ "SRMR")) |>
  mutate(est_print = papaja::printnum(est, gt1 = FALSE, digits = 3)) |>
  mutate(est_print = if_else(statistic == "df", as.character(est), est_print)) |>
  mutate(est_print = if_else(statistic == "p", papaja::printp(as.numeric(est_print)), est_print)) |>
  pivot_wider(id_cols = statistic, names_from = c(measure, categories), values_from = est_print)

>>>>

fit_df <- bind_rows(
  data.frame(as.list(fitMeasures(fit1A6))) |> mutate(measure = "age", categories = "6"),
  data.frame(as.list(fitMeasures(fit1A2))) |> mutate(measure = "age", categories = "2"),
  data.frame(as.list(fitMeasures(fit1G6))) |> mutate(measure = "height", categories = "6"),
  data.frame(as.list(fitMeasures(fit1G2))) |> mutate(measure = "height", categories = "2"),
  data.frame(as.list(fitMeasures(fit1Ge6))) |> mutate(measure = "weight", categories = "6"),
  data.frame(as.list(fitMeasures(fit1Ge2))) |> mutate(measure = "weight", categories = "2")
) |>
  pivot_longer(!c(measure, categories), names_to = "statistic", values_to = "est") |>
  filter(statistic %in% c("chisq.scaled", "pvalue.scaled", "df.scaled", "cfi.scaled", "rmsea.scaled", "srmr")) |>
  mutate(statistic = case_match(statistic, "chisq.scaled" ~ "$\\chi^2$", "pvalue.scaled" ~ "$p$", "df.scaled" ~ "$df$", "cfi.scaled" ~ "CFI", "rmsea.scaled" ~ "RMSEA", "srmr" ~ "SRMR")) |>
  mutate(est_print = papaja::printnum(est, gt1 = FALSE, digits = 3)) |>
  mutate(est_print = if_else(statistic == "df", as.character(est), est_print)) |>
  mutate(est_print = if_else(statistic == "p", papaja::printp(as.numeric(est_print)), est_print)) |>
  pivot_wider(id_cols = statistic, names_from = c(measure, categories), values_from = est_print)

### 2025-07-28 manuscript.qmd
Built site for gh-pages

---
title: "Item Construction Rules Revisited: Learnings from Measurement of Latent Variables with Gold-Standard Items"
shorttitle: "Measuring latent variables with gold-standard items"
date: 2025-07-18
date-modified: 2025-07-18
date-format: iso
author:
  - name: Kathryn Eichhorn
    orcid: 0000-0003-3676-9420
    role: 
      - conceptualization
      - investigation
      - resources
      - data curation
      - writing
    affiliations:
      - name: University of the Bundeswehr Munich
        department: Institute of Psychology
        city: Neubiberg
        country: Germany
  - name: Markus Bühner
    corresponding: true
    email: buehner@lmu.de
    orcid: 0000-0002-0597-8708
    role: 
      - formal analysis
      - supervision
      - writing
    affiliations:
      - id: "lmu"
        name: LMU Munich
        department: Department of Psychology
        address: Leopoldstr. 13
        city: D-80802 Munich
        country: Germany
        postal-code: 80802
  - name: Florian Pargent
    orcid: 0000-0002-2388-553X
    role:
      - formal analysis
      - software
      - validation
      - editing
    affiliations:
      - ref: lmu
  - name: Janika Saretzki
    orcid: 0000-0002-6536-8266
    role:
      - editing
    affiliations:
      - name: University of Graz
        department: Department of Psychology
        city: Graz
        country: Austria
      - name: Charlotte Fresenius University of Psychology
        city: Munich
        country: Germany
      - ref: lmu
  - name: Larissa Sust
    orcid: 0000-0002-3389-1626
    role:
      - editing
    affiliations:
      - ref: lmu
  - name: Jonas Hauck
    orcid: 0009-0002-8872-0530
    role:
      - editing
    affiliations:
      - id: "regen"
        name: University of Regensburg
        department: Faculty of Psychology
        city: Regensburg
        country: Germany
  - name: Sven Hilbert
    orcid: 0000-0001-5808-8357
    role:
      - conceptualization
      - supervision
      - editing
    affiliations:
      - ref: regen

>>>>

---
title: "Item Construction Rules Revisited: Learnings from Measurement of Latent Variables with Gold-Standard Items"
shorttitle: "Measuring latent variables with gold-standard items"
date: 2025-07-18
date-modified: 2025-07-28
date-format: iso
author:
  - name: Kathryn Eichhorn
    orcid: 0000-0003-3676-9420
    role: 
      - conceptualization
      - investigation
      - resources
      - data curation
      - writing
    affiliations:
      - name: University of the Bundeswehr Munich
        department: Institute of Psychology
        city: Neubiberg
        country: Germany
  - name: Markus Bühner
    corresponding: true
    email: buehner@lmu.de
    orcid: 0000-0002-0597-8708
    role: 
      - formal analysis
      - supervision
      - writing
    affiliations:
      - id: "lmu"
        name: LMU Munich
        department: Department of Psychology
        address: Leopoldstr. 13
        city: D-80802 Munich
        country: Germany
        postal-code: 80802
  - name: Florian Pargent
    orcid: 0000-0002-2388-553X
    role:
      - formal analysis
      - software
      - validation
      - editing
    affiliations:
      - ref: lmu
  - name: Janika Saretzki
    orcid: 0000-0002-6536-8266
    role:
      - editing
    affiliations:
      - name: University of Graz
        department: Department of Psychology
        city: Graz
        country: Austria
      - name: Charlotte Fresenius University of Psychology
        city: Munich
        country: Germany
      - ref: lmu
  - name: Larissa Sust
    orcid: 0000-0002-3389-1626
    role:
      - editing
    affiliations:
      - ref: lmu
  - name: Jonas Hauck
    orcid: 0009-0002-8872-0530
    role:
      - editing
    affiliations:
      - id: "regen"
        name: University of Regensburg
        department: Faculty of Psychology
        city: Regensburg
        country: Germany
  - name: Sven Hilbert
    orcid: 0000-0001-5808-8357
    role:
      - conceptualization
      - supervision
      - editing
    affiliations:
      - ref: regen
